---
title: "Dashboard Tour"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dashboard Tour}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.width = 8,
  fig.height = 4.5
)
```

`r4subui` provides an eight-tab Shiny dashboard for the R4SUB ecosystem.
This vignette shows what each tab produces using the built-in demo data.

```{r load}
library(r4subui)
library(r4subcore)
library(r4subscore)
library(r4subrisk)
library(r4subtrace)
library(r4subprofile)
library(r4subdata)

# Load demo evidence (250 rows, all 4 pillars)
data(evidence_pharma)
ev <- evidence_pharma
```

---

## Tab 1 — Overview

Shows the SCI score, decision band, and pillar score cards.

```{r overview, fig.cap="Overview: SCI and pillar scores"}
pillar_scores <- compute_pillar_scores(ev)
sci           <- compute_sci(pillar_scores)

# Pillar score cards
cols <- c(quality = "#2C6DB5", trace = "#27AE60",
          risk = "#E74C3C", usability = "#F39C12")
scores_vec <- setNames(pillar_scores$score, pillar_scores$pillar)

par(mfrow = c(1, 2), mar = c(4, 5, 3, 1))

# SCI gauge (simulated as a horizontal bar)
band_col <- switch(sci$band,
  ready      = "#27AE60",
  minor_gaps = "#F39C12",
  conditional = "#E67E22",
  high_risk  = "#E74C3C",
  "#2C6DB5"
)
barplot(sci$SCI, col = band_col, border = NA, xlim = c(0, 100),
        horiz = TRUE, axes = FALSE,
        main = paste0("SCI  =  ", round(sci$SCI, 1)))
axis(1, at = c(0, 50, 70, 85, 100))
abline(v = c(70, 85), lty = 2, col = "#888888")
mtext(sci$band, side = 1, line = 2.5, col = band_col, font = 2)

# Pillar bars
barplot(scores_vec[names(cols)], col = cols[names(scores_vec)],
        border = NA, ylim = c(0, 1), las = 1,
        ylab = "Score", main = "Pillar Scores")
abline(h = 0.85, lty = 2, col = "#555555")
```

---

## Tab 2 — Evidence Explorer

Filterable table of all evidence rows by domain, severity, and result.

```{r evidence-table}
# Distribution across domains and results
with(ev, table(indicator_domain, result))
```

```{r evidence-chart, fig.cap="Evidence: result distribution by pillar"}
domains <- c("quality", "trace", "risk", "usability")
results <- c("pass", "warn", "fail")
result_cols <- c(pass = "#27AE60", warn = "#F39C12", fail = "#E74C3C")

mat <- sapply(results, function(r)
  sapply(domains, function(d)
    sum(ev$indicator_domain == d & ev$result == r, na.rm = TRUE)
  )
)

par(mar = c(4, 7, 3, 6))
bp <- barplot(t(mat), beside = TRUE, col = result_cols,
              names.arg = domains, las = 1, border = NA,
              ylab = "Count", main = "Evidence Results by Pillar")
legend("topright", legend = results, fill = result_cols,
       border = NA, bty = "n", inset = c(-0.15, 0), xpd = TRUE)
```

---

## Tab 3 — Indicator Scores

Per-indicator severity-weighted scores with SCI loss contributors.

```{r indicators, fig.cap="Top 10 indicators by SCI loss contribution"}
explanation <- sci_explain(ev)
top_loss    <- head(explanation$top_loss, 10)

par(mar = c(4, 14, 3, 2))
barplot(rev(top_loss$loss), names.arg = rev(top_loss$indicator_name),
        horiz = TRUE, las = 1, col = "#E74C3C", border = NA,
        xlab = "SCI loss", main = "Top Loss Contributors")
```

---

## Tab 4 — Pillar Detail

Pillar contribution breakdown with result distribution per pillar.

```{r pillar-detail, fig.cap="Pillar contribution to SCI"}
contrib <- pillar_scores
contrib$contribution <- contrib$score * sci$config$pillar_weights[contrib$pillar]

par(mfrow = c(1, 2), mar = c(4, 6, 3, 1))
barplot(setNames(contrib$score, contrib$pillar),
        col = cols[contrib$pillar], border = NA,
        ylim = c(0, 1), las = 1, ylab = "Score",
        main = "Pillar Scores")

barplot(setNames(contrib$contribution, contrib$pillar),
        col = cols[contrib$pillar], border = NA, las = 1,
        ylab = "Contribution", main = "SCI Contribution")
```

---

## Tab 5 — Sensitivity Analysis

SCI stability under alternative pillar weight scenarios.

```{r sensitivity, fig.cap="SCI sensitivity to weight variations"}
sens      <- sci_sensitivity_analysis(ev)
scenarios <- sens$scenarios

par(mar = c(4, 11, 3, 2))
barplot(setNames(scenarios$sci, scenarios$scenario),
        horiz = TRUE, las = 1, col = "#2C6DB5", border = NA,
        xlim = c(0, 100), xlab = "SCI",
        main = "Sensitivity: SCI by Weight Scenario")
abline(v = sens$base_sci, lty = 2, col = "#E74C3C")
abline(v = c(70, 85), lty = 3, col = "#888888")
legend("bottomright", legend = c("Base SCI", "Bands"),
       lty = c(2, 3), col = c("#E74C3C", "#888888"), bty = "n")
```

---

## Tab 6 — Risk Register

Severity distribution and risk register evidence table.

```{r risk, fig.cap="Risk register: RPN distribution by severity level"}
data(risk_register_pharma)
rr     <- create_risk_register(risk_register_pharma)
scores_risk <- compute_risk_scores(rr)

dist     <- scores_risk$level_distribution
risk_cols <- c(low = "#27AE60", medium = "#F39C12",
               high = "#E67E22", critical = "#E74C3C")

par(mar = c(4, 5, 3, 2))
bp <- barplot(dist[names(risk_cols)],
              col = risk_cols[names(dist)], border = NA,
              ylab = "Count", las = 1,
              main = paste0("Risk Distribution  |  Mean RPN = ",
                            round(scores_risk$mean_rpn, 1)))
```

---

## Tab 7 — Traceability

Trace coverage summary, indicator scores, and result distribution.

```{r trace, fig.cap="Traceability: result distribution"}
data(adam_metadata); data(sdtm_metadata); data(trace_mapping)
ctx      <- r4sub_run_context(study_id = "CDISCPILOT01", environment = "review")
tm       <- build_trace_model(adam_metadata, sdtm_metadata, trace_mapping)
ev_trace <- trace_model_to_evidence(tm, ctx = ctx,
                                    source_name = "r4subtrace",
                                    source_version = "0.1.0")

res_counts <- table(ev_trace$result)
trace_cols <- c(pass = "#27AE60", warn = "#F39C12",
                fail = "#E74C3C", na = "#BDC3C7")

par(mar = c(4, 5, 3, 2))
barplot(res_counts[intersect(names(trace_cols), names(res_counts))],
        col    = trace_cols[intersect(names(trace_cols), names(res_counts))],
        border = NA, ylab = "Count", las = 1,
        main   = paste0("Traceability Results  |  ",
                        nrow(ev_trace), " indicators"))
```

---

## Tab 8 — Authority Profile

Regulatory profile selector with pillar weights and requirement coverage.

```{r authority, fig.cap="Pillar weight comparison across regulatory authorities"}
profiles <- list(
  FDA  = submission_profile("FDA",  "NDA"),
  EMA  = submission_profile("EMA",  "MAA"),
  PMDA = submission_profile("PMDA", "NDA_JP")
)

weight_mat <- sapply(profiles, function(p) p$pillar_weights)
pillars    <- rownames(weight_mat)

par(mar = c(4, 5, 3, 6))
barplot(weight_mat, beside = TRUE,
        col    = cols[pillars],
        border = NA, ylim = c(0, 0.5),
        ylab   = "Weight", las = 1,
        main   = "Pillar Weights by Regulatory Authority")
legend("topright", legend = pillars, fill = cols[pillars],
       border = NA, bty = "n", inset = c(-0.2, 0), xpd = TRUE)
```

---

## Launch the live dashboard

All of the above in one interactive browser interface:

```r
r4sub_app(evidence = evidence_pharma)
```
